Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-12 alloscore_manuscript/alloscore-application.Rnw
paragraph in discussion talking about whether the forecast adds useful information to an existing decision-making process. closes #44

>>>>

An additional limitation of the current work and opportunity for further investigation is to more carefully evaluate whether a forecast adds value to existing decision-making processes.
In the context of allocation-based decisions, standard procedures might involve simply extrapolating need based on a current observed data (similar to the `baseline' model presented above), with or without adjustments based on other political or real-world considerations.
For example, in many settings public health stakeholders will synthesize multiple sources of information, e.g. real-time data from a wide variety of quantitative and qualitative sources coupled with expert judgment based on a situational understanding of past and current experience.
The allocation score presented in this work assesses the optimality of the allocation based on an omniscient view of the future.
However, what we care about is whether a given forecast adds useful information to an existing decision-making process.
While the scoring procedures as presented do not directly address this question, they could be modified (say, by comparison to a `baseline` model) to quantify the benefit -if any- of using a forecast to inform a specific decision.
